---
title: "prospectorQualtrics Dashboard"
format: html
---

This is the dashboard for the Qualtrics Prospector.

## When to run it:

While the schedule says, "if I am alive, I will run a check 
for new responses every 10 minutes", the actual execution 
of the job is determined by SCRONTAB. This instead
says, "wake up this process every X amount of time by running
this script."

To add this to SCRONTAB, paste the code generated by `cronR` to your
SCRONTAB file:

```{r}
library(cronR)
library(here) # makes it easier to deal with path issues

cmd <- cron_rscript(
  here("run.R"), 
  workdir = here(),
  rscript_log = here("pipelines/logs/orchestrator.log"),
  log_append = TRUE,
  log_timestamp = TRUE
)
cron_cmd <- cron_add(command = cmd, frequency = 'minutely', id = 'test2', dry_run=TRUE, ask=FALSE)
```

With some SCRONTAB config we'll need:

```{r}
library(glue)
mail_user <- Sys.getenv("SLACK_EMAIL")
glue(
'#SCRON -J Maestro-prospectorQualtrics', 
'#SCRON -p hsph', 
'#SCRON --mem=1G', 
'#SCRON -t 00:10:00', 
'#SCRON --mail-type=FAIL,END', 
'#SCRON --mail-user={mail_user}', 
'{cron_cmd$min} {cron_cmd$hour} {cron_cmd$day_of_month} {cron_cmd$month} {cron_cmd$day_of_week} {cron_cmd$command}',
.sep = "\n")

```

## Run The Pipeline

The pipeline only needs the following:

```{r}
library(maestro)

schedule <- build_schedule()

run_schedule(
  schedule,
  orch_frequency = "10 minutes"
)
```


```{r}
glue("Last rendered: {Sys.time()}")
sessionInfo()
```