---
title: "Process Qualtrics Data Uploads"
embed-resources: true
filters:
    - sorting-hat
    - ripper
extensions:
    sorting-hat:
      keep:
        - r
      verbose: true
    ripper:
      include-yaml: false
      output-dir: "../R"
      output-name: "process_qualtrics_data"
      script-links-position: "none"
execute: 
  eval: false
params:
  testing: false
---

This prospector is designed to dynamically fetch
and ingest data from our Qualtrics survey projects.

## Setup

```{r}
library(dplyr)
library(stringr)
library(glue)
library(tidyr)
library(qualtRics)
library(googledrive)
library(googlesheets4)
library(here)
library(testthat)
library(logger)
box::use(
  R/downloaders[download_from_qualtrics]
)

if(!exists("params$testing")) {
  testing <- interactive()
}

log_file <- here("pipelines/logs/maestro.log")

if (testing) {
  log_threshold(DEBUG)
  log_appender(appender_tee(log_file))
  log_info("Running in testing mode: logs will be printed to console and saved to file.")
} else {
  log_threshold(INFO)
  log_appender(appender_file(log_file))
    log_info("Running in production mode: logs will be saved to file only.")
}
```

We first need to access the Qualtrics API to retrieve any new data:

```{r}
log_info("Setting up Qualtrics API connection...")

test_that("Qualtrics API credentials are set", {
  expect_true(Sys.getenv("QUALTRICS_API_KEY") != "")
  expect_true(Sys.getenv("QUALTRICS_BASE_URL") != "")
  expect_no_error(all_surveys())
})
```

We can access the exact Qualtrics project that has all
of our data upload records using its ID:

```{r}
log_info("Accessing Qualtrics project...")
qualtrics_project_id <- all_surveys() |>
  dplyr::filter(str_detect(name, "Data Intake Form")) |> 
  pull(id)

log_info("Qualtrics project ID retrieved")
survey_df <- fetch_survey(qualtrics_project_id)
log_info("Survey data retrieved: dimensions - {nrow(survey_df)} rows, {ncol(survey_df)} columns")
```

We should also get the corresponding google sheet that tracks whether or
not the response has been processed. Fortunately, we
have already set up a data engineering google service account
for all things Google Drive access:

```{r}
log_info("Setting up Google Sheets access...")

sa <- Sys.getenv("GOOGLEDRIVE_SERVICE_ACCOUNT_FILE")
gsheet <- Sys.getenv("GOOGLESHEETS_SHEET_URL")

test_that("Google API credentials are set", {

  expect_true(nzchar(sa))
  expect_true(file.exists(sa))
  expect_no_error(drive_auth(path = sa))
  expect_no_error(gs4_auth(path = sa))

})

sheet_df <- read_sheet(gsheet)

test_that("Google Sheet data retrieved correctly", {
  expect_true(nrow(sheet_df) > 0)
  expect_true(all(c("response_id", "processed") %in% colnames(sheet_df)))
})
```

## Processing

We process a response by checking whether the data is expected to
be larger than 50mb; if not, we can directly download it to 
the gold_mine qualtrics folder from the qualtrics response object ID.
So first, we must separate those two cases by joining the 
google sheet with the qualtrics survey data on the response 
ID, and then filtering for unprocessed responses:

```{r}
sheet_df |>
  mutate(
    gsheets_index = 1:n(), 
    processed = replace_na(processed, FALSE),
    data_gt_50_mb = case_when(
      data_gt_50_mb == "Yes" ~ TRUE,
      data_gt_50_mb == "No" ~ FALSE,
      TRUE ~ NA
    )) |>
  dplyr::filter(!processed) %>%
  full_join(., survey_df, by = join_by("response_id" == "ResponseId")) -> unprocessed_responses

log_info("Unprocessed responses identified: {nrow(unprocessed_responses)}")

unprocessed_responses |>
  dplyr::filter(!data_gt_50_mb) -> direct_download_candidates

unprocessed_responses |>
  dplyr::filter(data_gt_50_mb) -> globus_download_candidates

log_info("Download Candidates: {nrow(direct_download_candidates)} direct, {nrow(globus_download_candidates)} globus")
```

For responses with data larger than 50mb, we can use the globus path to
download the data to the gold_mine qualtrics folder, and for
responses with data smaller than 50mb, we can directly download it from the qualtrics response object ID to the gold_mine qualtrics folder. Here is the
case that we have data smaller than 50mb:

```{r}
if(nrow(direct_download_candidates) > 0){
  log_info("Processing direct downloads for {nrow(direct_download_candidates)} candidates...")

  direct_download_candidates %>%
    {
      if(testing){
        # just taking a sample for testing
        slice_sample(., n = min(3, nrow(.)))
      } else {
        .
      }
    } %>%
    rowwise() |>
    mutate(
      download_result = download_from_qualtrics(
        file_id = Q25_Id,
        filename = Q25_Name,
        qualtrics_project_id = qualtrics_project_id,
        response_id = response_id,
        response_date = StartDate,
        responder_id = case_when(
          !is.na(Q12) ~ Q12,
          !is.na(Q14) ~ Q14,
          !is.na(Q15) ~ Q15,
          !is.na(Q17) ~ Q17,
          !is.na(uploader_name) ~ uploader_name,
          TRUE ~ "Unknown"
        )
      )
    ) -> direct_download_results
  log_info("Direct download attempts completed for {nrow(direct_download_results)} candidates")
  test_that("Qualtrics direct download process completed successfully", {
    expect_true(all(!is.na(direct_download_results$download_result)))
    expect_true(all(file.exists(direct_download_results$download_result)))
  })
} else {
  log_info("No direct download candidates to process.")
  direct_download_results <- direct_download_candidates %>%
    mutate(download_result = NA_character_)
}
```

## Write Back Results

And after processing, we must update the google sheet to mark the response as processed:

```{r}
updated_sheet_df <- sheet_df |>
  left_join(
    direct_download_results |> select(response_id, download_result),
    by = join_by(response_id)
  ) |>
  mutate(
    processed = case_when(
      !is.na(download_result) ~ TRUE,
      TRUE ~ processed
    )
  ) %>%
  select(-download_result)

test_that("Google Sheet updated correctly after processing", {
  expect_shape(updated_sheet_df, nrow = nrow(sheet_df), ncol = ncol(sheet_df))
})

log_info("Google Sheet updated with processed status for direct downloads. Attempting to write back to Google Sheets...")
range_write(gsheet, updated_sheet_df, range = "A1", col_names = TRUE)
log_info("Google Sheet updated successfully with processed status for direct downloads.")
```

And with that, we're done!
