---
title: "Process Qualtrics Data Uploads"
embed-resources: true
filters:
    - sorting-hat
    - ripper
extensions:
    sorting-hat:
      keep:
        - r
      verbose: true
    ripper:
      include-yaml: false
      output-dir: "../R"
      output-name: "process_qualtrics_data"
      script-links-position: "none"
---

This prospector is designed to dynamically fetch
and ingest data from our Qualtrics survey projects.

## Setup

```{r}
library(dplyr)
library(glue)
library(qualtRics)
library(googlesheets4)
library(here)
```

We first need to access the Qualtrics API to retrieve any new data:

```{r}
print("Setting up Qualtrics API connection...")
connection_to_api <- "Connected"
```

We can access the exact Qualtrics project that has all
of our data upload records using its ID:

```{r}
print("Accessing Qualtrics project...")
qualtrics_project_id <- "1234567890"
print(paste("Project ID:", qualtrics_project_id))
survey_df <- data.frame(
  respondent_id = c("R1", "R2", "R3"),
  response = c("Yes", "No", "Yes"),
  data_gt_50mb = c(FALSE, FALSE, TRUE),
  data_path_globus = c(NA, NA, "globus://path/to/large/data/R3")
)
print("Survey data retrieved:")
```

We should also get the corresponding google sheet that tracks whether or
not the response has been processed:

```{r}
gsheet <- "url to google sheet"
sheet_df <- data.frame(
  respondent_id = c("R1", "R2", "R3"),
  processed = c(FALSE, FALSE, FALSE)
)
```

## Processing

We process a response by checking whether the data is expected to
be larger than 50mb; if not, we can directly download it to 
the gold_mine qualtrics folder from the qualtrics response object ID:

```{r}
sheet_df |>
    filter(!processed) |>
    left_join(survey_df, by = "respondent_id") |>
    rowwise() |>
    mutate(
        download_path = ifelse(data_gt_50mb == FALSE, paste0("gold_mine/qualtrics/", respondent_id, ".csv"), data_path_globus)
    ) |>
    ungroup() -> unprocessed_responses


print("Unprocessed responses with download paths:")
print(unprocessed_responses)
```

For responses with data larger than 50mb, we can use the globus path to
download the data to the gold_mine qualtrics folder, and for
responses with data smaller than 50mb, we can directly download it from the qualtrics response object ID to the gold_mine qualtrics folder. We can use
a global function called `download_data` that takes in the download path 
and the respondent ID to handle both cases:

```{r}
download_data <- function(download_path, respondent_id) {
    if (grepl("globus://", download_path)) {
        print(paste("Downloading large data for respondent", respondent_id, "from globus path:", download_path))
        # Code to download from globus would go here
    } else {
        print(paste("Downloading small data for respondent", respondent_id, "from Qualtrics response object ID:", download_path))
        # Code to download from Qualtrics would go here
    }
}

unprocessed_responses |>
    rowwise() |>
    mutate(
        download_result = download_data(download_path, respondent_id)
    ) -> processed_responses
```

And after processing, we must update the google sheet to mark the response as processed:

```{r}
updated_sheet_df <- sheet_df |>
    left_join(processed_responses, by = "respondent_id") |>
    mutate(processed = ifelse(!is.na(download_result), TRUE, FALSE))

print("Updated sheet with processed status:")
print(updated_sheet_df)
```

This pipeline will be run on a regular schedule, so technically
this counts as a dynamic daily ETL pipeline, so it should
be run with `maestro` and SCRONTAB. See this notebook for 
more details on how this was set up: [SCRONTAB Jobs with Maestro](10_pipelines.qmd).
