---
title: "Process Qualtrics Data Uploads"
embed-resources: true
filters:
    - sorting-hat
    - ripper
extensions:
    sorting-hat:
      keep:
        - r
      verbose: true
    ripper:
      include-yaml: false
      output-dir: "../R"
      output-name: "process_qualtrics_data"
      script-links-position: "none"
execute: 
  eval: false
params:
  testing: false
---

This prospector is designed to dynamically fetch
and ingest data from our Qualtrics survey projects.

## Setup

```{r}
library(dplyr)
library(stringr)
library(glue)
library(tidyr)
library(qualtRics)
library(googledrive)
library(googlesheets4)
library(here)
library(testthat)
library(logger)

if(!exists("params$testing")) {
  testing <- interactive()
}

log_file <- here("pipelines/logs/maestro.log")

if (testing) {
  log_threshold(DEBUG)
  log_appender(appender_tee(log_file))
  log_info("Running in testing mode: logs will be printed to console and saved to file.")
} else {
  log_threshold(INFO)
  log_appender(appender_file(log_file))
    log_info("Running in production mode: logs will be saved to file only.")
}
```

We first need to access the Qualtrics API to retrieve any new data:

```{r}
log_info("Setting up Qualtrics API connection...")

test_that("Qualtrics API credentials are set", {
  expect_true(Sys.getenv("QUALTRICS_API_KEY") != "")
  expect_true(Sys.getenv("QUALTRICS_BASE_URL") != "")
  expect_no_error(all_surveys())
})
```

We can access the exact Qualtrics project that has all
of our data upload records using its ID:

```{r}
log_info("Accessing Qualtrics project...")
qualtrics_project_id <- all_surveys() |>
  dplyr::filter(str_detect(name, "Data Intake Form")) |> 
  pull(id)

log_info("Qualtrics project ID retrieved")
survey_df <- fetch_survey(qualtrics_project_id)
log_info("Survey data retrieved: dimensions - {nrow(survey_df)} rows, {ncol(survey_df)} columns")
```

We should also get the corresponding google sheet that tracks whether or
not the response has been processed. Fortunately, we
have already set up a data engineering google service account
for all things Google Drive access:

```{r}
log_info("Setting up Google Sheets access...")

sa <- Sys.getenv("GOOGLEDRIVE_SERVICE_ACCOUNT_FILE")
gsheet <- Sys.getenv("GOOGLESHEETS_SHEET_URL")

test_that("Google API credentials are set", {

  expect_true(nzchar(sa))
  expect_true(file.exists(sa))
  expect_no_error(drive_auth(path = sa))
  expect_no_error(gs4_auth(path = sa))

})

sheet_df <- read_sheet(gsheet)

test_that("Google Sheet data retrieved correctly", {
  expect_true(nrow(sheet_df) > 0)
  expect_true(all(c("response_id", "processed") %in% colnames(sheet_df)))
})
```

## Processing

We process a response by checking whether the data is expected to
be larger than 50mb; if not, we can directly download it to 
the gold_mine qualtrics folder from the qualtrics response object ID:

```{r}
sheet_df |>
  mutate(
    gsheets_index = 1:n(), 
    processed = replace_na(processed, FALSE),
    data_gt_50_mb = case_when(
      data_gt_50_mb == "Yes" ~ TRUE,
      data_gt_50_mb == "No" ~ FALSE,
      TRUE ~ NA
    )) |>
  dplyr::filter(!processed) %>%
  full_join(., survey_df, by = join_by("response_id" == "ResponseId")) -> unprocessed_responses

log_info("Unprocessed responses identified: {nrow(unprocessed_responses)}")

unprocessed_responses |>
  dplyr::filter(!data_gt_50_mb) |>
  dplyr::select(response_id,)
    rowwise() |>
    mutate(
        download_path = ifelse(data_gt_50mb == FALSE, paste0("gold_mine/qualtrics/", respondent_id, ".csv"), data_path_globus)
    ) |>
    ungroup() -> unprocessed_responses


print("Unprocessed responses with download paths:")
print(unprocessed_responses)
```

For responses with data larger than 50mb, we can use the globus path to
download the data to the gold_mine qualtrics folder, and for
responses with data smaller than 50mb, we can directly download it from the qualtrics response object ID to the gold_mine qualtrics folder. We can use
a global function called `download_data` that takes in the download path 
and the respondent ID to handle both cases:

```{r}
download_data <- function(download_path, respondent_id) {
    if (grepl("globus://", download_path)) {
        print(paste("Downloading large data for respondent", respondent_id, "from globus path:", download_path))
        # Code to download from globus would go here
    } else {
        print(paste("Downloading small data for respondent", respondent_id, "from Qualtrics response object ID:", download_path))
        # Code to download from Qualtrics would go here
    }
}

unprocessed_responses |>
    rowwise() |>
    mutate(
        download_result = download_data(download_path, respondent_id)
    ) -> processed_responses
```

And after processing, we must update the google sheet to mark the response as processed:

```{r}
updated_sheet_df <- sheet_df |>
    left_join(processed_responses, by = "respondent_id") |>
    mutate(processed = ifelse(!is.na(download_result), TRUE, FALSE))

print("Updated sheet with processed status:")
print(updated_sheet_df)
```

This pipeline will be run on a regular schedule, so technically
this counts as a dynamic daily ETL pipeline, so it should
be run with `maestro` and SCRONTAB. See this notebook for 
more details on how this was set up: [SCRONTAB Jobs with Maestro](10_pipelines.qmd).
