---
title: "Downloaders"
embed-resources: true
filters:
    - sorting-hat
    - ripper
extensions:
    sorting-hat:
      keep:
        - r
      verbose: true
    ripper:
      include-yaml: false
      output-dir: "../R"
      output-name: "downloaders"
      script-links-position: "none"
execute: 
  eval: false
params:
  testing: false
---

In this notebook, we'll define some functions that
will help us download the data that was set up in the Qualtrics survey.

As a reminder, whenever we have data that the lab will want access
to, we ask lab members to fill out a data intake form on Qualtrics.
This form includes some metadata, but importantly, it differentiates
between data that is expected to be larger than 50mb, and data that is expected
to be smaller than 50mb. This is because Qualtrics has a file size 
limit of 50mb, so we have to use different download methods for data 
above and below that threshold. Below that threshold, we can directly
download the data. Above that threshold, and we assume that the uploader
followed the instructions in the survey and was able to upload their
data to our public globus endpoint, and then provided us with the file
name of their uploaded data, we can use that information to download the data from globus.

## Data < 50MB: Qualtrics

First, let's deal with the case that the data is expected to be smaller than 50mb.


```{r}
box::use(httr2)
box::use(readr)
box::use(lubridate)
box::use(fs)
box::use(here)
box::use(janitor)
box::use(glue)
box::use(purrr)
box::use(testthat)


#' Download an uploaded file from a Qualtrics survey response
#'
#' Downloads a file attached to a Qualtrics survey response using the Qualtrics
#' uploaded-files API endpoint. Files are staged under a date- and
#' responder-specific directory.
#'
#' @param file_id Character. Qualtrics uploaded file ID, usually beginning with
#'   `"F_"`.
#' @param filename Character. Output filename to use when saving the downloaded
#'   file.
#' @param qualtrics_project_id Character. Qualtrics survey ID, usually beginning
#'   with `"SV_"`.
#' @param response_id Character. Qualtrics response ID, usually beginning with
#'   `"R_"`.
#' @param response_date Date, POSIXct, or character coercible to a date. Used to
#'   partition staged downloads by response date.
#' @param responder_id Character. Identifier for the respondent or uploader.
#'   Used to create a responder-specific staging directory.
#' @param base_url Character. Qualtrics base URL. Defaults to the
#'   `QUALTRICS_BASE_URL` environment variable.
#' @param api_token Character. Qualtrics API token. Defaults to the
#'   `QUALTRICS_API_KEY` environment variable.
#' @param output_dir Character. Base staging directory for downloaded Qualtrics
#'   files.
#'
#' @return Character path to the downloaded file. Returns `NA_character_` if the
#'   download fails.
#'
#'
#' @examples
#' \dontrun{
#' download_from_qualtrics(
#'   file_id = "F_abc123",
#'   filename = "example.csv",
#'   qualtrics_project_id = "SV_abc123",
#'   response_id = "R_abc123",
#'   response_date = "2026-05-03",
#'   responder_id = "Example Responder"
#' )
#' }
#' @family Downloaders
#' @export
download_from_qualtrics <- function(
  file_id,
  filename,
  qualtrics_project_id,
  response_id,
  response_date,
  responder_id,
  base_url = Sys.getenv("QUALTRICS_BASE_URL"),
  api_token = Sys.getenv("QUALTRICS_API_KEY"),
  output_dir = here::here("data/staging/qualtrics")
) {
  required_args <- list(
    file_id = file_id,
    filename = filename,
    qualtrics_project_id = qualtrics_project_id,
    response_id = response_id,
    response_date = response_date,
    responder_id = responder_id,
    base_url = base_url,
    api_token = api_token,
    output_dir = output_dir
  )

  is_missing <- function(x) {
     is.null(x) || (length(x) == 1 && (is.na(x) || identical(x, "") || (is.character(x) && !nzchar(x))))
   }
  missing_args <- names(required_args)[vapply(required_args, is_missing, logical(1))]

  if (length(missing_args) > 0) {
    stop(
      "Missing required argument(s): ",
      paste(missing_args, collapse = ", "),
      call. = FALSE
    )
  }

  base_url <- sub("/+$", "", base_url)

  download_url <- glue::glue(
    "{base_url}/API/v3/surveys/{qualtrics_project_id}/responses/{response_id}/uploaded-files/{file_id}"
  )

  response_date <- lubridate::as_date(response_date)

  output_dir_final <- fs::path(
    output_dir,
    response_date,
    janitor::make_clean_names(responder_id)
  )

  fs::dir_create(output_dir_final)

  filename <- fs::path_file(filename)

  output_path <- fs::path(output_dir_final, filename)

  response <- httr2::request(download_url) |>
    httr2::req_headers(
      `X-API-TOKEN` = api_token,
      Accept = "application/octet-stream"
    ) |>
    httr2::req_retry(max_tries = 3) |>
    httr2::req_error(is_error = function(resp) FALSE) |>
    httr2::req_perform(path = output_path)

  status_code <- httr2::resp_status(response)

  if (status_code == 200 && fs::file_exists(output_path)) {
    message(glue::glue("File downloaded successfully to {output_path}"))
    return(as.character(output_path))
  }

  error_body <- tryCatch(
    httr2::resp_body_string(response),
    error = function(e) NA_character_
  )

  warning(
    glue::glue(
      "Failed to download file from Qualtrics. ",
      "Status code: {status_code}. ",
      "Output path: {output_path}. ",
      "Response body: {error_body}"
    ),
    call. = FALSE
  )

  NA_character_
}
```

This function will download a file from the 
given URL and save it to the specified output 
directory for staging. It assumes that the 
download_url is a direct link to the file from 
the qualtrics survey. Once the download has
been handled, the dataset will be assigned metadata
and downstream processing will be handled in the
rest of the pipeline.

```{r}
#| sorting-hat: remove
# Example:
example <- 2
qualtrics_project_id <- all_surveys() |>
    dplyr::filter(str_detect(name, "Data Intake Form")) |> 
    pull(id)
survey_df <- fetch_survey(qualtrics_project_id)
response_id <- survey_df |> slice(example) |> pull(ResponseId)
file_id <- survey_df |> slice(example) |> pull(Q25_Id)
response_date <- survey_df |> slice(example) |> pull(StartDate)
responder_id <- survey_df |> slice(example) |> pull(Q3)
filename <- survey_df |> slice(example) |> pull(Q25_Name)

download_from_qualtrics(
  file_id = file_id,
  filename = filename,
  qualtrics_project_id = qualtrics_project_id,
  response_id = response_id,
  response_date = response_date,
  responder_id = responder_id
)
```


Data Larger Than 50 MB: Globus

When a dataset is expected to exceed Qualtrics’ 50 MB upload limit, the uploader is instructed to upload the data to the lab’s Globus intake collection instead of attaching it directly to the survey.

During submission, the uploader is asked to place the dataset in a folder named after their Qualtrics response ID. This response ID serves as the primary key that links the uploaded files to the metadata collected in the survey.

Unlike files uploaded directly through Qualtrics, data uploaded through Globus already resides on Harvard’s HPC storage infrastructure. Specifically, the Globus collection used for intake is backed by a directory in the lab’s netscratch space. As a result, there is no external download step required.

The purpose of this function is therefore to:

1. Locate the intake folder corresponding to the survey response.
2. Verify that files have been uploaded.
3. Copy those files into the prospector staging area.
4. Return the staged dataset location for downstream processing.

Although the function is named download_from_globus_netscratch() for consistency with the Qualtrics workflow, it is technically performing a filesystem copy operation rather than a network download.

```{r}
#' Stage a dataset uploaded through the lab Globus intake collection
#'
#' Locates a dataset uploaded to the lab's Globus intake collection and copies
#' it into the prospector staging area. Uploads are expected to reside in a
#' directory named after the associated Qualtrics response ID. The function
#' verifies that the intake directory exists and contains files before copying
#' the contents to a response-specific staging directory.
#'
#' Unlike datasets uploaded directly through Qualtrics, Globus-uploaded data
#' already resides on Harvard's HPC storage infrastructure. As a result, this
#' function performs a filesystem copy operation rather than a network
#' download.
#'
#' @param response_id Character. Qualtrics response ID used to identify the
#'   corresponding Globus intake directory.
#' @param response_date Date, POSIXct, or character coercible to a date. Used
#'   to partition staged datasets by submission date.
#' @param responder_id Character. Identifier for the uploader. Used to create
#'   a responder-specific staging directory.
#' @param base_url Character. Path to the root Globus intake directory on the
#'   filesystem. Defaults to the lab's Globus-backed intake location.
#' @param output_dir Character. Base directory where staged datasets should be
#'   copied.
#'
#' @return Character path to the staged dataset directory. Returns
#'   `NA_character_` if one or more files fail to copy successfully.
#'
#' @details
#' The function assumes that:
#'
#' \itemize{
#'   \item Large datasets have been uploaded through the lab's Globus intake
#'     collection.
#'   \item Each upload resides in a directory named after the corresponding
#'     Qualtrics response ID.
#'   \item The intake collection is backed by a filesystem path accessible from
#'     the execution environment.
#' }
#'
#' @seealso [download_from_qualtrics()]
#'
#' @examples
#' \dontrun{
#' download_from_globus_netscratch(
#'   response_id = "R_123456789",
#'   response_date = "2026-05-03",
#'   responder_id = "Jane Doe"
#' )
#' }
#' @family Downloaders
#'
#' @export
download_from_globus_netscratch <- function(
  response_id,
  response_date,
  responder_id,
  base_url = "/n/netscratch/cgolden_lab/Lab/qualtrics_data_intake_folder",
  output_dir = here::here("data/staging/globus")
) {
  required_args <- list(
    response_id = response_id,
    response_date = response_date,
    responder_id = responder_id,
    base_url = base_url,
    output_dir = output_dir
  )

  is_missing <- function(x) {
     is.null(x) || (length(x) == 1 && (is.na(x) || identical(x, "") || (is.character(x) && !nzchar(x))))
   }
  missing_args <- names(required_args)[vapply(required_args, is_missing, logical(1))]

  if (length(missing_args) > 0) {
    stop(
      "Missing required argument(s): ",
      paste(missing_args, collapse = ", "),
      call. = FALSE
    )
  }

  download_url <- fs::fs_path(
    glue::glue(
      "{base_url}/{response_id}"
    )
  )

  message("Testing if Globus netscratch URL exists")

  fs::dir_exists(download_url) || stop(
    glue::glue("Globus netscratch URL does not exist: {download_url}"),
    call. = FALSE
  )

  response_date <- lubridate::as_date(response_date)

  output_dir_final <- fs::path(
    output_dir,
    response_date,
    janitor::make_clean_names(responder_id),
    response_id
  )

  fs::dir_create(output_dir_final)

  filenames <- fs::dir_ls(download_url, type = "any", recurse=TRUE) # this may appear as a singular character vector, but since it is a named char, you can use it as a list in subsequent map functions (ie it wont map over each character in the string, but rather treat the whole string as one element to map over)

  message("Testing if Globus netscratch URL contains files")
  length(filenames) > 0 || stop(
    glue::glue("Globus netscratch URL does not contain any files: {download_url}"),
    call. = FALSE
  )

  fs::dir_copy(download_url, output_dir_final, overwrite = TRUE)

  successfully_copied <- purrr::map_lgl(filenames, ~ fs::file_exists(fs::path(output_dir_final, fs::path_file(.x)))) |> 
    unlist()

   if(all(successfully_copied)) {
     message(glue::glue("All files copied successfully from {download_url} to {output_dir_final}"))
     return(as.character(output_dir_final))
   } else {
     warning(glue::glue("Some files failed to copy from {download_url} to {output_dir_final}"))
   }
  NA_character_
}
```

Awesome!
