---
title: "Downloaders"
embed-resources: true
filters:
    - sorting-hat
    - ripper
extensions:
    sorting-hat:
      keep:
        - r
      verbose: true
    ripper:
      include-yaml: false
      output-dir: "../R"
      output-name: "downloaders"
      script-links-position: "none"
execute: 
  eval: false
params:
  testing: false
---

In this notebook, we'll define some functions that
will help us download the data that was set up in the Qualtrics survey.

As a reminder, whenever we have data that the lab will want access
to, we ask lab members to fill out a data intake form on Qualtrics.
This form includes some metadata, but importantly, it differentiates
between data that is expected to be larger than 50mb, and data that is expected
to be smaller than 50mb. This is because Qualtrics has a file size 
limit of 50mb, so we have to use different download methods for data 
above and below that threshold. Below that threshold, we can directly
download the data. Above that threshold, and we assume that the uploader
followed the instructions in the survey and was able to upload their
data to our public globus endpoint, and then provided us with the file
name of their uploaded data, we can use that information to download the data from globus.

First, let's deal with the case that the data is expected to be smaller than 50mb.


```{r}
box::use(httr2)
box::use(readr)
box::use(lubridate)
box::use(fs)
box::use(here)
box::use(janitor)
box::use(glue)

#' Download an uploaded file from a Qualtrics survey response
#'
#' Downloads a file attached to a Qualtrics survey response using the Qualtrics
#' uploaded-files API endpoint. Files are staged under a date- and
#' responder-specific directory.
#'
#' @param file_id Character. Qualtrics uploaded file ID, usually beginning with
#'   `"F_"`.
#' @param filename Character. Output filename to use when saving the downloaded
#'   file.
#' @param qualtrics_project_id Character. Qualtrics survey ID, usually beginning
#'   with `"SV_"`.
#' @param response_id Character. Qualtrics response ID, usually beginning with
#'   `"R_"`.
#' @param response_date Date, POSIXct, or character coercible to a date. Used to
#'   partition staged downloads by response date.
#' @param responder_id Character. Identifier for the respondent or uploader.
#'   Used to create a responder-specific staging directory.
#' @param base_url Character. Qualtrics base URL. Defaults to the
#'   `QUALTRICS_BASE_URL` environment variable.
#' @param api_token Character. Qualtrics API token. Defaults to the
#'   `QUALTRICS_API_KEY` environment variable.
#' @param output_dir Character. Base staging directory for downloaded Qualtrics
#'   files.
#'
#' @return Character path to the downloaded file. Returns `NA_character_` if the
#'   download fails.
#'
#'
#' @examples
#' \dontrun{
#' download_from_qualtrics(
#'   file_id = "F_abc123",
#'   filename = "example.csv",
#'   qualtrics_project_id = "SV_abc123",
#'   response_id = "R_abc123",
#'   response_date = "2026-05-03",
#'   responder_id = "Example Responder"
#' )
#' }
#' @export
download_from_qualtrics <- function(
  file_id,
  filename,
  qualtrics_project_id,
  response_id,
  response_date,
  responder_id,
  base_url = Sys.getenv("QUALTRICS_BASE_URL"),
  api_token = Sys.getenv("QUALTRICS_API_KEY"),
  output_dir = here::here("data/staging/qualtrics")
) {
  required_args <- list(
    file_id = file_id,
    filename = filename,
    qualtrics_project_id = qualtrics_project_id,
    response_id = response_id,
    response_date = response_date,
    responder_id = responder_id,
    base_url = base_url,
    api_token = api_token,
    output_dir = output_dir
  )

  is_missing <- function(x) {
     is.null(x) || (length(x) == 1 && (is.na(x) || identical(x, "") || (is.character(x) && !nzchar(x))))
   }
  missing_args <- names(required_args)[vapply(required_args, is_missing, logical(1))]

  if (length(missing_args) > 0) {
    stop(
      "Missing required argument(s): ",
      paste(missing_args, collapse = ", "),
      call. = FALSE
    )
  }

  base_url <- sub("/+$", "", base_url)

  download_url <- glue::glue(
    "{base_url}/API/v3/surveys/{qualtrics_project_id}/responses/{response_id}/uploaded-files/{file_id}"
  )

  response_date <- lubridate::as_date(response_date)

  output_dir_final <- fs::path(
    output_dir,
    response_date,
    janitor::make_clean_names(responder_id)
  )

  fs::dir_create(output_dir_final)

  filename <- fs::path_file(filename)

  output_path <- fs::path(output_dir_final, filename)

  response <- httr2::request(download_url) |>
    httr2::req_headers(
      `X-API-TOKEN` = api_token,
      Accept = "application/octet-stream"
    ) |>
    httr2::req_retry(max_tries = 3) |>
    httr2::req_error(is_error = function(resp) FALSE) |>
    httr2::req_perform(path = output_path)

  status_code <- httr2::resp_status(response)

  if (status_code == 200 && fs::file_exists(output_path)) {
    message(glue::glue("File downloaded successfully to {output_path}"))
    return(as.character(output_path))
  }

  error_body <- tryCatch(
    httr2::resp_body_string(response),
    error = function(e) NA_character_
  )

  warning(
    glue::glue(
      "Failed to download file from Qualtrics. ",
      "Status code: {status_code}. ",
      "Output path: {output_path}. ",
      "Response body: {error_body}"
    ),
    call. = FALSE
  )

  NA_character_
}
```

This function will download a file from the 
given URL and save it to the specified output 
directory for staging. It assumes that the 
download_url is a direct link to the file from 
the qualtrics survey. Once the download has
been handled, the dataset will be assigned metadata
and downstream processing will be handled in the
rest of the pipeline.

```{r}
#| sorting-hat: remove
# Example:
example <- 2
qualtrics_project_id <- all_surveys() |>
    dplyr::filter(str_detect(name, "Data Intake Form")) |> 
    pull(id)
survey_df <- fetch_survey(qualtrics_project_id)
response_id <- survey_df |> slice(example) |> pull(ResponseId)
file_id <- survey_df |> slice(example) |> pull(Q25_Id)
response_date <- survey_df |> slice(example) |> pull(StartDate)
responder_id <- survey_df |> slice(example) |> pull(Q3)
filename <- survey_df |> slice(example) |> pull(Q25_Name)

download_from_qualtrics(
  file_id = file_id,
  filename = filename,
  qualtrics_project_id = qualtrics_project_id,
  response_id = response_id,
  response_date = response_date,
  responder_id = responder_id
)
```

