---
title: "Orchestrating The Maestro Job with SCRONTAB"
embed-resources: true
filters:
  - sorting-hat
  - ripper
extensions:
  sorting-hat:
    keep:
      - r
    verbose: true
  ripper:
    include-yaml: false
    output-dir: "../pipelines"
    output-name: "pipelines"
    script-links-position: "none"
---

This is a scrontab job that runs every 15 minutes to check for new
responses in the google sheet and process them accordingly. The job is set up using 
`maestro` and SCRONTAB, which allows us to schedule and automate the execution of this 
pipeline.

```{r}
library(maestro)
library(glue)
library(cronR)
library(here)
```

We created the job scaffold using `create_maestro`:

```{r}
#| eval: false
#| sorting-hat: remove
#create_maestro(".", overwrite = TRUE)
```

## What to run

This chunk sets up the pipelines for a `maestro` cronjob.
`maestro` recognizes the special comments in the function 
definition to determine the schedule and logging behavior of the 
job.

### Process Data

```{r}
#' Ferry Qualtrics Responses To The Gold Mine
#'
#' @maestroFrequency 1 hour
#' @maestroStartTime 2026-06-12
#' @maestroTz US/Eastern
#' @maestroLogLevel INFO
process_data_pipeline <- function() {

  print("Running the maestro pipeline...")
  source(here("R/process_qualtrics_data.R"))

}
```

This function will be executed according to the schedule defined in the comments. The content of this routine can
be viewed in the [Process Qualtrics Data Uploads notebook](01_process_qualtrics_data.qmd).

# Tracking: Git committing the logs

We can add a git commit and push step to as an additional pipeline,
saved in another notebook.

