---
title: "Orchestrating The Maestro Job with SCRONTAB"
format: html

---

This is a scrontab job that runs every 15 minutes to check for new
responses in the google sheet and process them accordingly. The job is set up using 
`maestro` and SCRONTAB, which allows us to schedule and automate the execution of this 
pipeline.

```{r}
library(maestro)
library(glue)
library(cronR)
library(here)
```

We created the job scaffold using `create_maestro`:

```{r}
#| eval: false
create_maestro(".", overwrite = TRUE)
```

## What to run:

This command sets up the necessary files for a `maestro` cronjob. Next, we export
the content of the job to the orchestrator.R file:


```{r}
#' Ferry Qualtrics Responses To The Gold Mine
#'
#' @maestroFrequency 10 minutes
#' @maestroStartTime 2026-06-12
#' @maestroTz UTC
#' @maestroLogLevel INFO

process_data_pipeline <- function() {

  print("Running the maestro pipeline...")
}
```

This function will be executed according to the schedule defined in the comments.

Next, we export the orchestrator.R file to the SCRONTAB:

```{r}
library(maestro)

schedule <- build_schedule()

output <- run_schedule(
  schedule,
  orch_frequency = "10 minutes"
)
```

This command schedules the job to look for new
responses every 10 minutes. 

## When to run it:

While the schedule says, "if I am alive, I will run a check 
for new responses every 10 minutes", the actual execution 
of the job is determined by SCRONTAB. This instead
says, "wake up this process every X amount of time by running
this script."

To add this to SCRONTAB, paste the code generated by `cronR` to your
SCRONTAB file:

```{r}
library(cronR)
library(here) # makes it easier to deal with path issues

cmd <- cron_rscript(
  here("orchestrator.R"), 
  workdir = here(),
  rscript_log = here("pipelines/logs/orchestrator.log"),
  log_append = TRUE,
  log_timestamp = TRUE
)
cron_cmd <- cron_add(command = cmd, frequency = 'minutely', id = 'test2', dry_run=TRUE, ask=FALSE)
```

With some SCRONTAB config we'll need:

```{r}
glue(
'#SCRON -J maestro_scrontab_job', 
'#SCRON -p hsph', 
'#SCRON --mem=1G', 
'#SCRON -t 00:10:00', 
'#SCRON --mail-type=FAIL,END', 
'#SCRON --mail-user=aaaapr3lk7gfdswioulcmvi3te@harvard.org.slack.com', 
'{cron_cmd$min} {cron_cmd$hour} {cron_cmd$day_of_month} {cron_cmd$month} {cron_cmd$day_of_week} {cron_cmd$command}',
.sep = "\n")

```

# Tracking: Git committing the logs

We can add a git commit and push step to as an additional pipeline,
saved in another notebook.

